\sysfull

### 2017-08-11 paper/evaluation.tex
work on evaluation section

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp} build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller. WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version 7. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. The RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github}. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance-controlled experiments, the WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code execution times have been measured using Salea~\cite{saleae} digital logic analyzer.

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was for continuous power experiments. We used internal timer for measuring run time. For harvested energy, we used the ThingMagic Astra-EX RFID reader with power levels of 30\,dBm. We used EDB~\cite{edb} for execution time measurement. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler. Both for Clang and LLVM we used version 3.8.0.

@@

We compare \sys against state of the art intermittent execution approach---Chain~\cite{chain}. We are not comparing \sys against DINO~\cite{dino} or Mementos~\cite{mementos} (Refer to Section~\ref{sec:background_consistency}), as (i) Chain is the only modular execution model available to which we can compare \sys, and (ii) Chain proves already its superiority over sequential model counterparts (i.e. DINO and Mementos).

We need to note that although another very relevant task-based runtime has been recently presented and referenced many times throughout this paper---Alpaca~\cite{alpaca} (written by the same group as Chain)---except the recently accepted manuscript we did not have the access to Alpaca's code during the preparation of this paper. Therefore Alpaca was excluded from the evaluation. \todo{Check if the line of argument is solid for the above paragraphs about not selecting DINO, Memenos and Aplaca}{Brandon}

@@

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Bitcount (bc) & 351 & 588 \\ %59\%
		Cold chain (cem) & 388 & 721 \\ %53\%
		Cuckoo (cuckoo) & 483 & 762 \\ %63\%
		RSA (rsa) & 887 & 1233 \\ %71\%
		Activity (ar) & 483 & 762 \\ %63\%
		DFT (dft) & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		Huffman (dd) & {} & {} \\ %Data decompression size: 100 bytes
		Selection sort (sort) & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

>>>>

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp} build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller. WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version 7. FET was also used as a power supply in non-intermittent power experiments. Energy consumption measurements provided in eariler sections were done with Carnegie Mellon's EDB~\cite{edb}. In experiments involving wireless power, the WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. The RFID reader is controlled by a PC running Ubuntu 10.4 executing an open source Python-based \emph{sllurp} library~\cite{sllrp_github}. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance-controlled experiments, the WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code execution times were measured using Salea~\cite{saleae} logic analyzer.

We also used an alternative setup where the MSP-TS430RGZ48C launchpad was used for continuous power experiments. We used internal timer for measuring run time\todo{how about EDB?}{Kiwan}. For harvested energy, we used the ThingMagic Astra-EX RFID reader set at 30\,dBm transmission power\todo{say what antenna are you using with what gain}{Kiwan}. Applications were cross-compiled using GCC and Clang, so that we can use LLVM for \sys compiler. Version 3.8.0 was used for both Clang and LLVM.

@@

We compare \sys against state-of-the-art task-based runtime Chain~\cite{chain}. We are not comparing \sys against DINO~\cite{dino} or Mementos~\cite{mementos} (Refer to Section~\ref{sec:background_consistency}), as (i) Chain is the only modular execution model available to which we can compare \sys, and (ii) Chain proved already its superiority over sequential model counterparts (i.e. DINO and Mementos)\footnote{We need to note that although another very relevant task-based runtime has been recently presented and referenced many times throughout this paper---Alpaca~\cite{alpaca} (written by the same group as Chain)---except the recently accepted manuscript we did not have the access to Alpaca's code during the preparation of this paper. Therefore Alpaca was excluded from the evaluation.}.

@@

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Nickname (abbreviation) & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		Bitcount (bc) & 351 & 588 \\ %59\%
		Cold chain (cem) & 388 & 721 \\ %53\%
		Cuckoo (cuckoo) & 483 & 762 \\ %63\%
		RSA (rsa) & 887 & 1233 \\ %71\%
		Activity (ar) & 483 & 762 \\ %63\%
		DFT (dft) & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		Huffman (dd) & {} & {} \\ %Data decompression size: 100 bytes
		Selection sort (sort) & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}
